The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2018-08-08 script/en/chapters/what-is-sage.tex
CT book (de+en): Corrected all broken links and fixed some few typos.

%% \centering statt \begin{center} ... \end{center}, da dies zusätzlich vertical space erzeugt.
\noindent In the meantime there are lots of PDF and HTML documents about using SageMath, so we name only a few of them as a good starting point\footnote{%
- ``Library'': {\centering \url{http://www.sagemath.org/library/index.html}},\\
- ``Documentation Project'': {\centering \url{http://wiki.sagemath.org/DocumentationProject}},\\
- ``Teaching'': {\centering \url{http://wiki.sagemath.org/Teaching_with_SAGE}}.
}.

\noindent With respect to studying cryptography, SageMath modules can be used
to complement a first course in cryptography\footnote{%
- Module sources in the directory \url{SAGE_ROOT/devel/sage-main/sage/crypto}.

\noindent\hangindent=6pt\makebox[6pt][l]{-}Overview, what crypto currently is in SageMath:\\
   \url{http://www.sagemath.org/doc/reference/sage/crypto/}

@@

   % Leerzeile am Ende nötig, sonst hat die zweite Zeile KEINEN hängenden Einzug?! (TODO_LaTeX)
   % Dadurch aber mehr Abstand von Seitennummer als sonst!
}.

\noindent Comprehensive introductions into cryptography are in this
footnote\footnote{%
- David Kohel's notes from 2008 are a ready cource\\
{\centering \url{http://www.sagemath.org/library/crypto.pdf} }
or the same eventually newer at\\
{\centering \url{http://sage.math.washington.edu/home/wdj/teaching/kohel-crypto.pdf} }.\\
- ``Introduction to Cryptography with Open-Source Software, a very good book
  from Alasdair McAndrew, CRC, 2011\\
}.

% ---------------------------------------------------------------------------
\section*{SageMath user interfaces}
SageMath is available free of charge and can be downloaded from the
following website:
\begin{center}
  \url{http://www.sagemath.org} \\
\end{center}
The default interface to SageMath is {\bf command line} based, as shown in
figure~\ref{fig:sage_cmd_interfaces}. However, there is a
graphical user interface to the software as well in the form of the
SageMath notebook (see figure~\ref{fig:sage_gui_interfaces}). We can even
use SageMath {\bf notebooks}\footnote{%
Further details about SageMath notebooks can be found at 
chapter~\ref{ec:Sage_Massierer} 
(``\nameref{ec:Implementing-for-Education}''
$\Rightarrow$ ``\nameref{ec:Sage_Massierer}'').
                      }
online at different servers, without having to install SageMath locally, e.g:
\begin{center}
\url{http://www.sagenb.org} or\\
\url{http://sage.mathematik.uni-siegen.de:8000}
\end{center}

@@

\noindent To program and test SageMath code using an editor there are two useful commands:
\verb!load()! and \verb!attach()!\footnote{%
See SageMath tutorial about Programming, chapter ``Loading and Attaching Sage files'',\\
\url{http://www.sagemath.org/doc/tutorial/programming.html\#loading-and-attaching-sage-files}.}.\\
Suppose you have a function definition like this:
\begin{Verbatim}%
   [fontsize=\footnotesize]
   def function(var1):
       r"""
       DocText.
       """
       ...
       return (L)
\end{Verbatim}
\noindent which has been saved to the file \texttt{primroots.sage}.

>>>>

%% \centering statt \begin{center} ... \end{center}, da dies zusätzlich vertical space erzeugt.
\noindent In the meantime there are lots of PDF and HTML documents about using SageMath, so we name only a few of them as a good starting point\footnote{%
- ``Library'': {\centering \url{http://www.sagemath.org/library.html}},\\
- ``Documentation Project'': {\centering \url{http://wiki.sagemath.org/DocumentationProject}},\\
- ``Teaching'': {\centering \url{http://wiki.sagemath.org/Teaching_with_SAGE}}.
}.

\noindent With respect to studying cryptography, SageMath modules can be used
to complement a first course in cryptography\footnote{%
\noindent\hangindent=6pt\makebox[6pt][l]{-}Overview, what crypto currently is in SageMath:\\
   \url{http://www.sagemath.org/doc/reference/sage/crypto/}

@@

   % TODO: hängender Einzug und Leerzeile (TODO_LaTeX)
   % Dadurch aber mehr Abstand von Seitennummer als sonst! ?
}.

\noindent Comprehensive introductions into cryptography are in this
footnote\footnote{%
- David Kohel's notes from 2008 are a ready cource\\
{\centering \url{http://www.sagemath.org/files/kohel-book-2008.pdf} }
or the same newer (from 2015) at\\
{\centering \url{http://iml.univ-mrs.fr/~kohel/tch/M2-CryptoSymetrique/crypto.pdf} }.\\
- ``Introduction to Cryptography with Open-Source Software, a very good book
  from Alasdair McAndrew, CRC, 2011\\
}.

% ---------------------------------------------------------------------------
\section*{SageMath user interfaces}
SageMath is available free of charge and can be downloaded from the
following website:
\begin{center}
  \url{http://www.sagemath.org} \\
\end{center}
The default interface to SageMath is {\bf command line} based, as shown in
figure~\ref{fig:sage_cmd_interfaces}. However, there is a
graphical user interface to the software as well in the form of the
SageMath notebook (see figure~\ref{fig:sage_gui_interfaces}). We can even
use SageMath {\bf notebooks}\footnote{%
Further details about SageMath notebooks can be found at 
chapter~\ref{ec:Sage_Massierer} 
(``\nameref{ec:Implementing-for-Education}''
$\Rightarrow$ ``\nameref{ec:Sage_Massierer}'').
                      }
online at different servers, without having to install SageMath locally, e.g:
\begin{center}
\url{http://sagecell.sagemath.org/} or\\
\url{https://cocalc.com/}
\end{center}

@@

\noindent To program and test SageMath code using an editor there are two useful commands:
\verb!load()! and \verb!attach()!\footnote{%
See SageMath tutorial about Programming, chapter ``Loading and Attaching Sage files'',\\
\url{http://doc.sagemath.org/html/en/tutorial/programming.html}.}.\\
Suppose you have a function definition like this:
\begin{Verbatim}%
   [fontsize=\footnotesize]
   def function(var1):
       r"""
       DocText.
       """
       ...
       return (L)
\end{Verbatim}
\noindent which has been saved to the file \texttt{primroots.sage}.
